\documentclass[10pt,a4paper]{article}

% Standard packages
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}

% Colors - modern dark gray/charcoal scheme with dark blue accents
\definecolor{darkgray}{RGB}{45,45,45}
\definecolor{mediumgray}{RGB}{100,100,100}
\definecolor{lightgray}{RGB}{150,150,150}
\definecolor{darkblue1}{RGB}{20,50,80}
\definecolor{darkblue2}{RGB}{30,60,95}
\definecolor{darkblue3}{RGB}{40,70,110}
\definecolor{darkblue4}{RGB}{50,80,120}

% Custom formatting
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=16pt,topsep=0.8pt,itemsep=0.5pt,parsep=0pt,label=\textbullet}

% Modern section formatting
\newcommand{\cvsection}[1]{%
  \vspace{1em}
  {\large\bfseries\color{darkgray} #1}\\
  \rule{\textwidth}{1pt}
}

% Professional header design - centered with dark blue accents
\newcommand{\cvheader}[6]{%
  \begin{center}
    \vspace{0.2em}
    {\LARGE\bfseries\color{darkblue1} #1} \quad {\large\color{darkblue2} #2}\\[0.25em]
    {\footnotesize\color{darkblue3} #3 \quad $|$ \quad #4 \quad $|$ \quad #5 \quad $|$ \quad #6}\\[0.6em]
  \end{center}
}

% Keywords - two rows with dark blue tones
\newcommand{\cvkeywords}[2]{%
  \begin{center}
    {\footnotesize\bfseries\color{darkblue3} #1}\\[0.25em]
    {\footnotesize\color{darkblue4} #2}\\[0.4em]
  \end{center}
}

% Experience entry - minimal italics
\newcommand{\cventry}[4]{%
  \vspace{0.12em}
  \textbf{#2} \hfill \textbf{\textcolor{darkgray}{#1}}\\
  #3 \hfill \textbf{\textcolor{mediumgray}{#4}}
}

\begin{document}

% Header - professional design
\cvheader{Marc Vernet}{SOFTWARE ENGINEER}
  {(+34) 650117126}{mrcvs31@gmail.com}{marc-vernet.me}
  {github.com/marcvernet31 \quad $|$ \quad linkedin.com/in/marc-vernet}

% Experience
\cvsection{WORK EXPERIENCE}
\cventry{Jul. 2022--Present}{Software Development Engineer}{Amazon Luxembourg}{Luxembourg}
\begin{itemize}[topsep=0pt]
  \item Delivered \$3.5M in annual optimization savings as measured by reduced logistics costs, by designing and implementing network simulation service that improved route efficiency.
  \item Enabled 30\% reduction in development time as measured by feature delivery cycles, by developing internal agentic AI tooling with \textbf{Rust} used across all of Amazon.
  \item Improved code maintainability and reduced technical debt as measured by bug reduction and test coverage, by orchestrating \textbf{Java-to-Kotlin} migration for 10,000+ lines achieving 95\% test coverage.
  \item Reduced infrastructure maintenance time by 50\% as measured by operational overhead, by implementing \textbf{CI/CD} pipeline with \textbf{AWS CDK} enabling automated deployments.
  \item Maintained 99.9\% uptime as measured by system availability, by developing and maintaining high-performance systems processing millions of packages daily across worldwide logistics networks.
  \item Reduced system downtime by 40\% as measured by incident frequency, by implementing operational support processes and resolving critical bugs across services used by 500+ daily users.
  \item Accelerated team onboarding by 50\% as measured by time-to-productivity, by mentoring 2 interns to full-time conversion and producing comprehensive technical documentation.
  \item Delivered 95\% of sprint commitments as measured by sprint velocity, by serving as Scrum Manager and conducting 200+ code reviews ensuring code quality standards.
  \item Reduced system latency by 35\% as measured by p99 response times, by implementing distributed caching layer using \textbf{Redis} and optimizing data access patterns across \textbf{microservices} architecture.
\end{itemize}
\vspace{0.25em}

\cventry{Jan. 2022--Jul. 2022}{Business Intelligence Engineer}{Amazon Luxembourg}{Luxembourg}
\begin{itemize}[topsep=0pt]
  \item Reduced false positives by 60\% as measured by alert accuracy, by implementing \textbf{ML}-powered infrastructure monitoring service analyzing 1M+ data points daily for anomaly detection.
  \item Reduced average query time by 40\% as measured by database performance metrics, by optimizing \textbf{SQL} queries for \textbf{AWS RDS} cluster serving 5 internal organizations.
  \item Eliminated 40+ hours of manual work monthly as measured by time savings, by automating administrative tasks using \textbf{AWS Lambda} and \textbf{Python} with comprehensive \textbf{CI/CD} pipeline.
  \item Enabled data-driven workforce decisions as measured by dashboard usage, by developing HR BI dashboards serving 10,000 monthly users and providing actionable insights for leadership.
  \item Improved anomaly detection response time by 80\% as measured by alert latency, by designing and developing responsive UI with \textbf{React} and \textbf{AWS} supporting 50 daily users with real-time alerts.
\end{itemize}
\vspace{0.25em}

\cventry{Jan. 2021--Jan. 2022}{Research Intern}{Universitat Rovira i Virgili (URV)}{Barcelona, Spain}
\begin{itemize}[topsep=0pt]
  \item Improved prediction accuracy by 25\% as measured by model performance metrics, by developing \textbf{ML} predictive models for air pollution levels processing daily measurements across 12 monitoring stations.
  \item Contributed to published research as measured by peer-reviewed publication, by co-authoring academic paper and scientific journal article in environmental research advancing air quality monitoring methodologies.
\end{itemize}
\vspace{0.25em}

% Technical Skills
\cvsection{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=16pt,topsep=0pt,itemsep=0.6pt]
  \item \textbf{Languages:} Kotlin, TypeScript, Java, Rust, Python, SQL, C++
  \item \textbf{Frameworks:} React, Angular, Node.js, SpringBoot, Django, Rails, Nginx, LaTeX
  \item \textbf{Technologies:} RESTful APIs, Microservices, Linux/Unix, MySQL, PostgreSQL
  \item \textbf{Software Engineering:} System Design, CI/CD, DevOps, Test-Driven Development (TDD), Agile/Scrum
  \item \textbf{Cloud:} AWS CDK, AWS CI/CD pipelines, AWS Redshift, serverless development, AWS Lambda, CloudWatch
\end{itemize}
\vspace{0.25em}

% Certifications
\cvsection{CERTIFICATIONS}
{\footnotesize
\textbf{AWS Solutions Architect (SAA-C03)} \quad $|$ \quad \textbf{AWS Certified Cloud Practitioner} \quad $|$ \quad \textbf{Cisco CCNA, Introduction to Networks}
}
\vspace{0.4em}

% Education
\vspace{0.5em}
{\large\bfseries\color{darkgray} EDUCATION}\\
\rule{\textwidth}{1pt}
\textbf{B.S. in Data Science and Engineering} \hfill \textbf{\textcolor{darkgray}{Sep. 2018--May 2022}}\\
Polytechnic University of Catalonia (UPC) \hfill \textbf{\textcolor{mediumgray}{Barcelona, Spain}}
\vspace{0.2em}

\end{document}
