\documentclass[10pt,a4paper]{article}
\input{base/preamble}

\begin{document}

% Override title to match AI engineering roles
\cvheader{Marc Vernet}{AI ENGINEER}
  {(+34) 650117126}{mrcvs31@gmail.com}{marc-vernet.me}
  {github.com/marcvernet31 \quad $|$ \quad linkedin.com/in/marc-vernet}

% ─── WORK EXPERIENCE ─────────────────────────────────────────────────────────
\cvsection{WORK EXPERIENCE}

% Enginy — cherry-picked 3 bullets (RAG bullet excluded until metric is confirmed)
\cventry{Feb. 2026--Present}{Software Engineer}{Enginy}{Luxembourg}
\begin{itemize}[topsep=0pt]
  \item Eliminated manual prospect research by developing \textbf{Chrome Extension} in \textbf{TypeScript} that automates profile data extraction from \textbf{LinkedIn} and web sources, delivering 500+ structured lead records per day into backend enrichment pipelines.
  \item Improved lead data quality by 25\% by designing and implementing async enrichment pipelines in \textbf{Node.js} that aggregate, validate, and merge prospect data from 10+ external sources using \textbf{PostgreSQL}.
  \item Accelerated go-to-market tooling by building \textbf{TypeScript} integrations with CRM platforms and third-party data APIs, enabling automated multi-source lead enrichment across sales campaign workflows.
\end{itemize}
\vspace{0.15em}

% Amazon SDE — AI tooling promoted to #1, then systems/scale bullets
\cventry{Jul. 2022--Feb. 2026}{Software Development Engineer}{Amazon Luxembourg}{Luxembourg}
\begin{itemize}[topsep=0pt]
  \item Built internal agentic \textbf{AI} tooling in \textbf{Rust} that automates code generation, test writing, and documentation using \textbf{LLM} pipelines, deployed across all of Amazon's engineering teams.
  \item Reduced \$3.5M in annual logistics costs by designing and implementing network simulation service that models route optimization algorithms, analyzes real-time traffic patterns, and evaluates distribution center capacity across European fulfillment network.
  \item Reduced system latency by 35\% by implementing distributed caching layer using \textbf{Redis} and optimizing data access patterns with connection pooling across \textbf{microservices} architecture.
  \item Reduced infrastructure maintenance time by 50\% by implementing \textbf{CI/CD} pipeline with \textbf{AWS CDK} for automated deployments and infrastructure-as-code provisioning across microservices architecture.
\end{itemize}
\vspace{0.15em}

% Amazon BI — ML monitoring + Python automation
\cventry{Jan. 2022--Jul. 2022}{Business Intelligence Engineer}{Amazon Luxembourg}{Luxembourg}
\begin{itemize}[topsep=0pt]
  \item Reduced false positives by 60\% by implementing \textbf{ML}-powered infrastructure monitoring service using time-series forecasting and anomaly detection, analyzing 1M+ data points daily from server metrics, network traffic, and application logs.
  \item Eliminated 40+ hours of manual work monthly by automating data pipeline monitoring, report generation, and access provisioning using \textbf{AWS Lambda} and \textbf{Python} with \textbf{CI/CD} pipeline.
\end{itemize}
\vspace{0.15em}

\input{content/experience/urv-research}
\vspace{0.15em}

% ─── TECHNICAL SKILLS ────────────────────────────────────────────────────────
% Reordered for AI / LLM / Python-first roles
\cvsection{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=16pt,topsep=0pt,itemsep=0.6pt]
  \item \textbf{Languages:} Python, TypeScript, Kotlin, Rust, Java, SQL
  \item \textbf{AI / LLM:} LLM integration (OpenAI, Anthropic APIs), agentic AI pipelines, prompt engineering, ML (time-series forecasting, anomaly detection, ensemble methods)
  \item \textbf{Frameworks:} \textbf{FastAPI}, React, Node.js, SpringBoot, scikit-learn, Nginx
  \item \textbf{Technologies:} RESTful APIs, microservices, PostgreSQL, Redis, Linux/Unix
  \item \textbf{Cloud:} AWS CDK, AWS Lambda, AWS Redshift, AWS RDS, CloudWatch, serverless development
  \item \textbf{Engineering:} System Design, CI/CD, DevOps, Test-Driven Development (TDD), Agile/Scrum
\end{itemize}
\vspace{0.15em}

% ─── CERTIFICATIONS ──────────────────────────────────────────────────────────
\input{content/certifications}

% ─── EDUCATION ───────────────────────────────────────────────────────────────
\input{content/education}

\end{document}
