% ─── EXPERIENCE: Amazon — Software Development Engineer ───────────────────────
% Full bullet pool. Variants can \input this file for all bullets,
% or copy-paste a subset directly into a variant for fine-grained control.

\cventry{Jul. 2022--Present}{Software Development Engineer}{Amazon Luxembourg}{Luxembourg}
\begin{itemize}[topsep=0pt]
  \item Reduced \$3.5M in annual logistics costs (transportation, fuel, warehouse operations) by designing and implementing network simulation service that models route optimization algorithms, analyzes real-time traffic patterns, and evaluates distribution center capacity to improve delivery efficiency across European fulfillment network.
  \item Collaborated in developing internal agentic AI tooling with \textbf{Rust} that automates code generation, test writing, and documentation, used across all of Amazon's engineering teams.
  \item Improved code maintainability and reduced technical debt by orchestrating \textbf{Java-to-Kotlin} migration for 10,000+ lines of logistics service code, implementing null-safety patterns and coroutine-based async processing with 95\% test coverage.
  \item Reduced infrastructure maintenance time by 50\% by implementing \textbf{CI/CD} pipeline with \textbf{AWS CDK} for automated deployments and infrastructure-as-code provisioning across microservices architecture.
  \item Maintained 99.9\% uptime by developing and maintaining high-performance logistics orchestration systems processing millions of packages daily, handling real-time inventory updates and shipment routing across worldwide fulfillment networks.
  \item Reduced system downtime by 40\% by implementing operational support processes, automated health checks, and resolving critical bugs across internal tooling services.
  \item Reduced system latency by 35\% by implementing distributed caching layer using \textbf{Redis} and optimizing data access patterns with connection pooling across \textbf{microservices} architecture.
\end{itemize}
